---
title: "Problem Set Number"
author: "Your Name"
date: "Enter the Due Date"
output:
  html_document: default
---

People you worked with on the assignment: Bob Smith, Joe Tilly


***To compile the Markdown document into an html, click on the "Knit" icon in the toolbar at the top of your upper-left RStudio window..***


```{r setup, include=FALSE}
## Because include=FALSE, won't appear in your compiled document

## This chunk sets global options for the full document, such as how big the figures should be
knitr::opts_chunk$set(echo = TRUE,  fig.width = 5, fig.height = 4, fig.align = "center", tidy = TRUE)
```



***The text below gives you examples of how to format problem set code. You can edit to match your own needs. For example, in the initial assignment, I ask you to title the section Problem 2.1 instead of Problem 1.***

# Problem 1

As above, you can use the \# symbol to indicate a new section has started in your document: \# Problem 1, for example (See raw .Rmd file). If you use multiple \#\#, this will create a subsection.

## Problem 1.1

What makes R Markdown useful is that you can include code chunks in the document (see the raw .Rmd file).

Example: Adding numbers.
```{r}
2 + 2
```

I can write the answer to this in plain language. Answer: 4.

# Problem 2

When you use Markdown for problem sets, please still include both the raw code and written answers, even if the answer may seem obvious within the code.
```{r}
sum53 <- 5 + 3
sum53
```

Written answer: The answer to this is 8.


# Problem 3
Markdown will also print to the pdf the output of plots you create. For example, suppose an assignment asked you to make a histogram of a vector with numbers 10,20,30,40.
```{r}
hist(c(10, 20, 30, 40),
     main = "Toy plot",
     xlab = "Toy numbers")
```


